Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-02-06 paper/ms.tex
2 new paragraphs. line breaks added

Figure \label{figure:landscape} presents the regions in the parameter space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of $P>0.1$. Each panel corresponds to the three different ways of grouping the mock fields. In the case of the methods {\tt{MatchObs}} and {\tt{RandomObs}} the color code indicates the fraction of these 15 mock surveys with with $P>0.1$. The third panel shows the result for the method {\tt{FullVolume}}, in this case the color code correspond to the value of $P$ for a given model.

@@

There are some models where the KS test yield values of $P\sim 1$. To illustrate the kind of success represented by these models, we have selected these best ones in the case of the method {\tt{MatchObs}}. Figure XXX shows in the main panel the spatial distribution of the mock surveys, the smaller panel shows the corresponding surface density distribution and the observational constraint.

@@

%\begin{figure}
% \input{plots/TCF}
%\end{figure}

\section{Conclusions}

>>>>

Figure \label{figure:landscape} presents the regions in the parameter
space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of
$P>0.1$. Each panel corresponds to the three different ways of
grouping the mock fields. In the case of the methods {\tt{Match}}
and {\tt{Random}} the color code indicates the fraction of these 15
mock surveys with with $P>0.1$. The third panel shows the result for
the method {\tt{Full}}, in this case the color code correspond
to the value of $P$ for a given model.

@@

The two {\tt match} and {\tt random} methods present the highest
number of matching mock surveys in the medium mass regime. However, it
is important to keep in mind that not all the mock surveys for a
sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
modest seems to be consistent with observations. This shows that the
cosmic variance is still present on the physical scales probed by
observations.

... Figure presents the results for two mock fields for the same
model, the two have extreme values for the KS test.

Conversely here are different models where the KS test yield values of
$P\sim 1$. To illustrate the kind of success represented by these
models, we have selected these best ones in the case of the method
{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
distribution of the mock surveys, the smaller panel shows the
corresponding surface density distribution and the observational
constraint.

@@

\section{Conclusions}
In this letter we have presented new method to estimate preferred
mass for dark matter halos hosting Lyman Alpha Emitters at
$z=3.1$. The method is based on making an estimate of the cosmic
variance from different observed fields. Based on a Nbody simulation,
we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
host LAEs being compatible witht the cosmic variance constraints.

We have used a large volume cosmological N-body simulation that allows
us to extract $210$ sub-boxes each of which has a comparable
volume to the field of view observed by Yamada et al. 2012. The
comparison of the observed number density distribution against the
results from our model is based on three different ways of
constructing mock surveys. The first reproduces the spatial
correlation between the $12$ observational fields, the second breaks
this spatial correlation while keeping the number of fields and the
third one simply includes all the $210$ sub-boxes.
